Exploring fishing data

### 2022-12-22 ocean_disclosure_project.Rmd
back ups: graphs for paper, some notes, and data collection script

apo |> select(permit_holder) |> unique()
```

>>>>

apo |> select(permit_holder) |> unique()
```
```{r}
## from Alaskan pollock permits:
## files ending in cp are catcher processors, endin gin cv are catcher vessels
fls <- dir_ls("data/Alaska_pollock/")

dat <- fls |> str_subset("afa") |> 
    map(.f = function(x) read_csv(x, skip=1) |> janitor::clean_names()) |> 
    map(select, owner_name) |> 
    bind_rows() |> 
    unique()
dat

write_csv(dat, file = "fishing_companies_alaskan-pollock.csv")
```

### Extract companies

```{r}

companies <- bind_rows(
    anch |> select(company = titular_de_cuota_ltp) |> unique(),
    sard |> select(company = titular_de_cuota_ltp) |> unique(),
    sardesp |> select(company = titular_de_cuota_ltp) |> unique()
) |> unique()

companies 
```

```{r}
write_csv(companies, file = "fishing_comps_sardina-anchoveta.csv")
```
